{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-24 thesis/quicksand.tex
fix algorithm KwIn stuff

\begin{algorithm}[h]
	\SetKwInOut{Input}{Input}
	\Input{$j$, the currently-running job}
	\Input{\AllPPs, the set of all known preemption points} %, sorted by decreasing heuristic priority}
	\eIf{$\exists p \in \AllPPs . p \not\in \GetPPSet{j}$}{
		return NewJob(\AllPPs) // New maximal state space
	}{
		return $j$ // $j$ is still maximal
	}
	\caption{Na\"ive Iterative Deepening method}
	\label{alg:algorithm0}
\end{algorithm}

@@

\newcommand\AllJobs{\ensuremath{\mathcal{J}}}
\begin{algorithm}[h]
	\SetKwInOut{Input}{Input}
	\Input{$j_0$, the currently-running job}
	\Input{\AllJobs, the set of all existing (or completed) jobs}
	\Input{$\alpha$, an instruction reported by the MC as part of a racing access pair}
	\If{$\forall j \in \AllJobs,$
	\GetPPSet{$j_0$} $\cup$ $\alpha$
	$\not\subseteq$
	\GetPPSet{$j$}
	}{
		AddNewJob(\GetPPSet{$j_0$} $\cup$ $\alpha$, HeuristicPriority($\alpha$)) \\
	}
	\If{$\forall j \in \AllJobs,$ \GetPPSet{$j$} $\neq \{yield, \alpha\}$}{
		AddNewJob($\{yield, \alpha\}$, HeuristicPriority($\alpha$))
	}
	\caption{Adding new jobs with data-race preemption points.}
	\label{alg:handledatarace}
\end{algorithm}

@@

\begin{algorithm}[t]
	\SetKwInOut{Input}{Input}
	%\textbf{Function} GetBestJob($j_0$, PendingJobs, SuspendedJobs): \\
	\Input{$j_0$, the currently-running job}
	\Input{\PendingJobs, the list of pending jobs, sorted by decreasing heuristic priority}
	\Input{\SuspendedJobs, the list of already-suspended jobs, sorted by increasing ETA}
	\Input{$T$, the remaining time in the CPU budget}
	\If{\GetETA{$j_0$} $<$ HeuristicETAFactor $\times$ $T$}{
		return $j_0$ // Common case: job is expected to finish.
	}
	\ForEach{job $j_P \in$ \PendingJobs}{
		// Don't run a pending job if a subset of it is already suspended; its ETA would be at least as bad. \\
		\If {$\forall j_S \in$ \SuspendedJobs, \GetPPSet{$j_S$} $\not\subset$ \GetPPSet{$j_P$}}{
			return $j_P$
		}
	}
	%// no pending jobs; maybe resume a suspended job \\
	\ForEach{job $j_S \in$ \SuspendedJobs}{
		\If{\GetPPSet{$j_0$} $\not\subset$ \GetPPSet{$j_S$}
			$\land$
			\GetETA{$j_0$} $>$ \GetETA{$j_S$}}{
			// If a subset of $j_S$ is also suspended, don't run the larger one first. \\
			\If{$\forall j_{S2} \in$ \SuspendedJobs, \GetPPSet{$j_{S2}$} $\not\subset$ \GetPPSet{$j_S$}}{
				return $j_S$
			}
		}
	}
	return $j_0$ // \GetETA{$j_0$} was bad, but no other $j$ was better.
	\caption{Suspending exploration of a state space in favor of a potentially smaller one.}
	\label{alg:shouldworkblock}
\end{algorithm}

>>>>

\begin{algorithm}[t]
	\KwIn{$j$, the currently-running job}
	\KwIn{\AllPPs, the set of all known preemption points} %, sorted by decreasing heuristic priority}
	\eIf{$\exists p \in \AllPPs . p \not\in \GetPPSet{j}$}{
		return NewJob(\AllPPs) // New maximal state space; switch to it
	}{
		return $j$ // $j$ is still maximal
	}
	\caption{Na\"ive Iterative Deepening method}
	\label{alg:algorithm0}
\end{algorithm}

@@

\newcommand\AllJobs{\ensuremath{\mathcal{J}}}
\begin{algorithm}[h]
	\KwIn{$j_0$, the currently-running job}
	\KwIn{\AllJobs, the set of all existing (or completed) jobs}
	\KwIn{$\alpha$, an instruction reported by the model checker as part of a data race}
	\If{$\forall j \in \AllJobs,$
	\GetPPSet{$j_0$} $\cup$ $\alpha$
	$\not\subseteq$
	\GetPPSet{$j$}
	}{
		AddNewJob(\GetPPSet{$j_0$} $\cup$ $\alpha$, HeuristicPriority($\alpha$)) \\
	}
	\If{$\forall j \in \AllJobs,$ \GetPPSet{$j$} $\neq \{yield, \alpha\}$}{
		AddNewJob($\{yield, \alpha\}$, HeuristicPriority($\alpha$))
	}
	\caption{Adding new jobs with data-race preemption points.}
	\label{alg:handledatarace}
\end{algorithm}

@@

\begin{algorithm}[t]
	%\textbf{Function} GetBestJob($j_0$, PendingJobs, SuspendedJobs): \\
	\KwIn{$j_0$, the currently-running job}
	\KwIn{\PendingJobs, the list of pending jobs, sorted by decreasing heuristic priority}
	\KwIn{\SuspendedJobs, the list of already-suspended jobs, sorted by increasing ETA}
	\KwIn{$T$, the remaining time in the CPU budget}
	\If{\GetETA{$j_0$} $<$ HeuristicETAFactor $\times$ $T$}{
		return $j_0$ // Common case: job is expected to finish.
	}
	\ForEach{job $j_P \in$ \PendingJobs}{
		// Don't run a pending job if a subset of it is already suspended; its ETA would be at least as bad. \\
		\If {$\forall j_S \in$ \SuspendedJobs, \GetPPSet{$j_S$} $\not\subset$ \GetPPSet{$j_P$}}{
			return $j_P$
		}
	}
	%// no pending jobs; maybe resume a suspended job \\
	\ForEach{job $j_S \in$ \SuspendedJobs}{
		\If{\GetPPSet{$j_0$} $\not\subset$ \GetPPSet{$j_S$}
			$\land$
			\GetETA{$j_0$} $>$ \GetETA{$j_S$}}{
			// If a subset of $j_S$ is also suspended, don't run the larger one first. \\
			\If{$\forall j_{S2} \in$ \SuspendedJobs, \GetPPSet{$j_{S2}$} $\not\subset$ \GetPPSet{$j_S$}}{
				return $j_S$
			}
		}
	}
	return $j_0$ // \GetETA{$j_0$} was bad, but no other $j$ was better.
	\caption{Suspending exploration of a job in favor of a potentially smaller one.}
	\label{alg:shouldworkblock}
\end{algorithm}
